Preliminary Thesis Defence

### 2013-11-14 draft.Rnw
text changes

\chapter{Additional South African Evidence on Pensions and Child Growth}

@@

This paper looks at the effect of the gender of pension recipients on the growth of children in their household in South Africa. The approach
is very similar to Duflo (\href{http://www.jstor.org/discover/10.2307/117257}{2000},\href{http://wber.oxfordjournals.org/content/17/1/1}{2003}). The deviation from international standards \href{http://www.who.int/childgrowth/en/}{Child Growth Standards} for weight-for-height and length-for-age are computed as z-scores. These are then compared for different pension recipient status.

@@

The South African pension is a useful variable to measure income because of its criteria. Besides a maximum level of income, the only criterium is the age of a person. Because of this the status as a recipient is quite exogenous and there are few selection bias problems. The problematic difference between the eligibility age of men and women was eliminated between the two surveys which creates an interesting natural experiment.

@@

\paragraph{On limiting the sample}
page 1480, line 17. ``When we restricted the sample to exclude deaths after September 1864 and captures prior to October 1864 because only the dying may have been left at Andersonville once men were transferred out, our results remained unchanged. The derivative of the coefficient on the number of men in the company was 0.003 (sdev=0.001) and the derivative of the coefficient on the number of men in the regiment with the same last name was 0.035 (sdev=0.007).

@@

\begin{refsection}
\chapter{Morris Shin Currency Attacks}
blafslkfjas;lfkjasfd
\parencite{morris1998unique}
\printbibliography
\end{refsection}

>>>>

\begin{refsection}
\chapter{Additional South African Evidence on Pensions and Child Growth}

@@

This paper looks at the effect of the gender of pension recipients on the growth of children in their household in South Africa. The approach
is very similar to Duflo (\href{http://www.jstor.org/discover/10.2307/117257}{2000},\href{http://wber.oxfordjournals.org/content/17/1/1}{2003}). The deviation from international standards \href{http://www.who.int/childgrowth/en/}{Child Growth Standards} for weight-for-height and length-for-age are computed as z-scores. These are then compared for different pension recipient status and gender.

@@

The South African pension is a interesting variable to measure income because of its criteria. Besides a maximum level of income, the only criterium is the age of a person. Because of this the status as a recipient is quite exogenous and there are few selection bias issues. The problematic difference between the eligibility age of men and women was eliminated between the two surveys which creates an interesting natural experiment.

@@

\paragraph{On limiting the sample}
page 1480, line 17. ``When we restricted the sample to exclude deaths after September 1864 and captures prior to October 1864 because only the dying may have been left at Andersonville once men were transferred out, our results remained unchanged. The derivative of the coefficient on the number of men in the company was 0.003 (sdev=0.001) and the derivative of the coefficient on the number of men in the regiment with the same last name was 0.035 (sdev=0.007).''

@@

\chapter{Morris Shin Currency Attacks}

blafslkfjas;lfkjasfd

\parencite{morris1998unique}
